Svyset analysis

### 2018-07-28 CW3CB3_4.Rmd
tables 1 added

---
title: "NDNS multilevel LCA CW2CB2 or CW2CB3"
author: "Chaochen Wang"
date: "19 July 2018"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "NDNS multilevel LCA CW2CB2 or CW2CB3"
author: "Chaochen Wang"
date: "Created at 2018-7-19, Updated at `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

### 2018-07-28 paper/Chapters/Chapter3.tex
tables 1 added

@@

>>>>

\begin{table}
	\rowcolors{2}{gray!6}{white}	
	\caption{\label{tab:}Means, percentages, and 95\% CIs of the characteristics by multilevel latent class analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
		\centering
		\fontsize{9}{10}\selectfont
		\begin{tabular}[t]{lccc}
			\hiderowcolors
			\toprule
			Variables & Latent class = 1 & Latent class = 2 & P value \textsuperscript{*}\\
			\midrule
			\showrowcolors
			Total (\%) & 66.4  (64.8 , 68.1) & 33.6  (31.9 , 35.2) & \\
			Countries (\%) &  &  & \\
			\hspace{1em}England & 83.1  (80.9 , 85.1) & 85.4  (83.0 , 87.5) & 0.203\\
			\hspace{1em}Northern Ireland & 3.0  (2.3 , 3.9) & 2.3  (1.7 , 3.1) & \\
			\hspace{1em}Scotland & 8.9  (7.2 , 11.0) & 7.7  (5.9 , 9.9) & \\
			\hspace{1em}Wales & 5.0  (4.1 , 6.0) & 4.6  (3.6 , 6.0) & \\
			Age (years) & 47.3 (46.4, 48.2) & 50.1 (49.1, 51.1) & < 0.001\\
			Sex (\%) &  &  & \\
			\hspace{1em}Men & 47.3  (45.2 , 49.5) & 51.0  (48.1 , 53.9) & 0.048\\
			\hspace{1em}Women & 52.7  (50.5 , 54.8) & 49.0  (46.1 , 51.9) & \\
			Survey years (\%) &  &  & \\
			\hspace{1em}1 & 13.1 (10.8, 15.8) & 15.0 (12.1, 18.5) & 0.365\\
			\hspace{1em}2 & 12.3 (10.1, 14.9) & 11.9 (9.4, 14.2) & \\
			\hspace{1em}3 & 12.0 (9.8, 14.8) & 10.4 (8.2, 13.1) & \\
			\hspace{1em}4 & 13.2 (10.9, 16.0) & 11.4 (9.0, 14.2) & \\
			\hspace{1em}5 & 13.0 (10.8, 15.7) & 13.9 (11.1, 17.3) & \\
			\hspace{1em}6 & 12.0 (9.9, 14.4) & 11.1 (8.8, 13.9) & \\
			\hspace{1em}7 & 12.3 (10.1,14.9) & 13.5 (10.9, 16.7) & \\
			\hspace{1em}8 & 12.0 (9.9, 14.5) & 12.8 (10.3, 15.8) & \\
			BMI (kg/m\textsuperscript{2}) & 27.2 (26.9, 27.5) & 27.7 (27.5, 28.1) & 0.007\\
			WC (cm) & 92.6 (91.9, 93.3) & 94.2 (93.1, 95.2) & 0.013\\
			Smoking status (\%) &  &  & \\
			\hspace{1em}Current & 19.8  (18.2 , 21.4) & 23.8 (21.3 , 26.5) & < 0.001\\
			\hspace{1em}Ex-smoker & 22.5  (20.8 , 24.2) & 28.0 (25.4 , 30.7) & \\
			\hspace{1em}Never & 57.8  (55.7 , 59.8) & 48.2 (45.3 , 51.1) & \\
			Current drinking status (\%) &  &  & \\
			\hspace{1em}Yes & 23.1  (21.3 , 25.1) & 11.1  (9.5 , 13.0) & < 0.001\\
			Hypertension (\%) \textsuperscript{\dag} &  &  & \\
			\hspace{1em}Yes & 27.4  (25.0 , 29.9) & 32.6  (29.3 , 36.1) & 0.012\\
			Total energy intake (KJ) & 7425.7 (7323.7, 7527.8) & 8149.9 (7997.3, 8302.7) & < 0.001\\
			Carbohydrate intake (g) & 226.0 (222.8, 229.3) & 210 (206.1, 213.9) & < 0.001\\
			Carbohydrate
			percent (\%) \textsuperscript{\ddag} & 48.3 (48.0, 48.6) & 40.9 (40.6, 41.3) & < 0.001\\
			Glucose (mmol/l) & 5.13 (5.09, 5.17) & 5.17 (5.11, 5.22) & 0.292\\
			A1C (\%) & 5.49 (5.47, 5.52) & 5.47 (5.44,5.51) & 0.264\\
			DM \textsuperscript{\S} & 4.1  (3.1 , 5.3 ) & 5.9  (4.3 , 8.0 ) & 0.061\\
			Physical
			activity (hours/day) \textsuperscript{\P} & 1.51 (1.39, 1.63) & 1.64 (1.45, 1.82) & 0.244\\
			\bottomrule
			\multicolumn{4}{l}{\textit{Note: }}\\
			\multicolumn{4}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\ 
			\multicolumn{4}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\ 
			\multicolumn{4}{l}{DM, diabetes mellitus.}\\
			\multicolumn{4}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\  
			\multicolumn{4}{l}{the others are weighted by individual weights.}\\
			\multicolumn{4}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
			\multicolumn{4}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes.}\\
			\multicolumn{4}{l}{For categorical variables, differences between latent classes were assessed using the adjusted}\\
			\multicolumn{4}{l}{Pearson Chi-2 test for survey data.}\\
			\multicolumn{4}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood}\\
			\multicolumn{4}{l}{pressure >= 90 mmHg, or under treatment for hypertension.}\\
			\multicolumn{4}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
			\multicolumn{4}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
			\multicolumn{4}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\
			\multicolumn{4}{l}{during the survey.}\\
		\end{tabular}
	\rowcolors{2}{white}{white}
	\end{table}

@@

\rowcolors{2}{gray!6}{white}

\begin{table}

	\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95\% CIs of the characteristics by latent class growth analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lcccc}
		\hiderowcolors
		\toprule
		Variables & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\
		\midrule
		\showrowcolors
		Total (\%) & 28.4 (26.8, 30.1) & 7.0 (6.2, 7.9) & 64.6 (62.9, 66.2) & \\
		Countries (\%) &  &  &  & \\
		\hspace{1em}England & 81.4 (78.5, 84.0) & 87.5 (82.9, 91.0) & 84.6 (82.5, 86.4) & 0.004\\
		\hspace{1em}Northern Ireland & 3.9 (2.9, 5.1) & 0.6 (0.3, 1.2) & 2.5 (2.0, 3.2) & \\
		\hspace{1em}Scotland & 9.5 (7.4, 12.3) & 6.2 (3.5, 10.6) & 8.3 (6.7, 10.3) & \\
		\hspace{1em}Wales & 5.2 (4.1, 6.6) & 5.7 (3.8, 8.5) & 4.6 (3.8, 5.6) & \\
		Age (years) & 43.8 (42.4, 45.1) & 49.1 (47.2, 50.9) & 50.1 (49.3, 50.9) & < 0.001\\
		Sex (\%) &  &  &  & \\
		\hspace{1em}Men & 50.6 (47.3, 53.9) & 49.6 (43.7, 55.4) & 47.6 (45.4, 49.7) & 0.273\\
		\hspace{1em}Women & 49.4 (46.1, 52.7) & 50.4 (44.6, 56.3) & 52.4 (50.3, 54.6) & \\
		Survey years (\%) &  &  &  & \\
		\hspace{1em}1 & 11.4 (8.8, 14.7) & 17.1 (12.4, 23.3) & 14.4 (11.9, 17.4) & 0.002\\
		\hspace{1em}2 & 10.1 (7.8, 13.1) & 18.3 (13.3, 24.7) & 12.4 (10.2, 15.0) & \\
		\hspace{1em}3 & 13.9 (10.8, 17.7) & 9.1 (5.7, 14.1) & 10.7 (8.6, 13.1) & \\
		\hspace{1em}4 & 10.9 (8.5, 13.9) & 13.8 (9.7, 19.4) & 13.2 (10.9, 16.0) & \\
		\hspace{1em}5 & 13.5 (10.6, 17.0) & 12.8 (8.4, 19.1) & 13.3 (11.0, 16.1) & \\
		\hspace{1em}6 & 12.8 (10.1, 16.1) & 8.7 (5.7, 12.9) & 11.5 (9.5, 13.9) & \\
		\hspace{1em}7 & 14.3 (11.5, 17.6) & 9.5 (6.5, 13.8) & 12.4 (10.2, 15.0) & \\
		\hspace{1em}8 & 13.2 (10.5, 16.4) & 10.5 (7.4, 14.8) & 12.1 (9.9, 14.6) & \\
		BMI (kg/m\textasciicircum{}2) & 27.5 (27.1, 27.9) & 27.0 (26.4, 27.6) & 27.4 (27.2, 27.6) & 0.433\\
		WC (cm) & 93.3 (92.1, 94.5) & 92.9 (90.9, 95.0) & 93.1 (92.3, 93.8) & 0.928\\
		Smoking status (\%) &  &  &  & \\
		\hspace{1em}Current & 24.1 (21.5, 27.0) & 30.0 (24.8, 35.8) & 18.8 (17.2, 20.6) & < 0.001\\
		\hspace{1em}Ex-smoker & 20.0 (17.6, 22.6) & 27.5 (22.4, 33.2) & 25.9 (24.1, 27.7) & \\
		\hspace{1em}Never & 55.9 (52.7, 59.0) & 42.5 (36.6, 48.7) & 55.3 (53.2, 57.4) & \\
		Current drinking status (\%) &  &  &  & \\
		\hspace{1em}Yes & 24.6 (21.7, 27.7) & 18.3 (14.0, 23.6) & 16.8 (15.3, 18.4) & < 0.001\\
		Hypertension (\%) \textsuperscript{\dag} &  &  &  & \\
		\hspace{1em}Yes & 25.9 (22.3, 29.9) & 31.8 (25.3, 39.1) & 30.4 (27.9 32.8) & 0.111\\
		Total energy intake (KJ) &  \Centerstack{ 6713.8 \\ (6575.7, 6851.8)}   &  \Centerstack{ 9256.0 \\ (8850.8, 9661.2)}   &  \Centerstack{7916.9 \\ (7814.0, 8019.9)}     & < 0.001\\
		Carbohydrate intake (g) & 192.9 (188.5, 197.3) & 275.6 (263.4, 287.8) & 226.9 (223.9, 229.9) & < 0.001\\
		Carbohydrate
		percent (\%) \textsuperscript{\ddag} & 45.8 (45.3, 46.4) & 47.4 (46.5, 48.3) & 45.6 (45.3, 45.9) & 0.001\\
		Glucose (mmol/l) & 5.16 (5.08, 5.23) & 5.09 (5.00, 5.18) & 5.14 (5.10, 5.19) & 0.537\\
		A1C (\%) & 5.47 (5.42, 5.51) & 5.48 (5.42, 5.54) & 5.49 (5.47. 5.52) & 0.403\\
		DM \textsuperscript{\S} & 5.9 (4.2, 8.2) & 1.1 (0.2, 5.2) & 4.7 (3.6, 6.0) & 0.053\\
        Physical activity (hs/day) \textsuperscript{\P}& 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\
		\bottomrule
		\multicolumn{5}{l}{\textit{Note: }}\\
		\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey}\\
		\multicolumn{5}{l}{rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c;}\\
		\multicolumn{5}{l}{DM, diabetes mellitus; h, hour.}\\
		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\
		\multicolumn{5}{l}{the others are weighted by individual weights.}\\
		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\   
		\multicolumn{5}{l}{with Bonferroni correction to account for multiple testing across >2 classes.}\\
		\multicolumn{5}{l}{For categorical variables, differences between latent classes were assessed}\\
		\multicolumn{5}{l}{using the adjusted Pearson Chi-2 test for survey data.}\\
		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic}\\ 
		\multicolumn{5}{l}{blood pressure >= 90 mmHg, or under}\\
		\multicolumn{5}{l}{treatment for hypertension.}\\
		\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
		\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\ 
		\multicolumn{5}{l}{during the survey.}\\
	\end{tabular}
\end{table}

\rowcolors{2}{white}{white}

### 2018-07-28 paper/Tables/2by2Table1.tex
tables 1 added

% Chapter Template

\chapter{Results} % Main chapter title

\label{Chapter 3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Main Section 1}

@@

	\caption{\label{tab:}Means, percentages, and 95\% CIs of the characteristics by multilevel latent class analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}

@@

		\fontsize{9}{10}\selectfont
		\begin{tabular}[t]{lccc}

@@

			BMI (kg/m\textsuperscript{2}) & 27.2 (26.9, 27.5) & 27.7 (27.5, 28.1) & 0.007\\

@@

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Main Section 2}

@@

	\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95\% CIs of the characteristics by latent class growth analysis memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}

@@

	\begin{tabular}[t]{lcccc}

@@

		Total energy intake (KJ) &  \Centerstack{ 6713.8 \\ (6575.7, 6851.8)}   &  \Centerstack{ 9256.0 \\ (8850.8, 9661.2)}   &  \Centerstack{7916.9 \\ (7814.0, 8019.9)}     & < 0.001\\

@@

        Physical activity (hs/day) \textsuperscript{\P}& 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\

@@

		\multicolumn{5}{l}{DM, diabetes mellitus; h, hour.}\\

@@

		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\   
		\multicolumn{5}{l}{with Bonferroni correction to account for multiple testing across >2 classes.}\\
		\multicolumn{5}{l}{For categorical variables, differences between latent classes were assessed}\\

@@

		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic}\\ 
		\multicolumn{5}{l}{blood pressure >= 90 mmHg, or under}\\

@@

		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\ 
		\multicolumn{5}{l}{during the survey.}\\

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
    \setmainfont[]{Arial}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=0.8in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Tables in the project},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Tables in the project}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\begin{document}
\maketitle

@@

\caption{\label{tab:unnamed-chunk-1}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}

@@

\begin{tabular}[t]{llll}

@@

BMI (kg/m\textasciicircum{}2) & 27.2 (26.9, 27.5) & 27.7 (27.5, 28.1) & 0.007\\

@@

@@

\caption{\label{tab:unnamed-chunk-2}Means, percentages, and 95 percent CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}

@@

\begin{tabular}[t]{lllll}

@@

Total energy intake (KJ) & 6713.8 (6575.7, 6851.8) & 9256.0 (8850.8, 9661.2) & 7916.9 (7814.0, 8019.9) & < 0.001\\

@@

activity (hours/day) \textsuperscript{\P} & 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\

@@

\multicolumn{5}{l}{DM, diabetes mellitus.}\\

@@

\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to}\\
\multicolumn{5}{l}{account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed}\\

@@

\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under}\\

@@

\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey.}\\

@@

\end{document}

### 2018-07-28 results/Summary of survey analysis.Rmd
tables 1 added

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate percent (%) [note]")
dt[35, 1] <- c("DM [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%."), 
               notation = "symbol")
```

@@

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate percent (%) [note]")
dt[35, 1] <- c("DM [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%."), 
               notation = "symbol")
```

>>>>

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
dt[35, 1] <- c("DM [note]")
dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%.", 
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
               notation = "symbol")
```

@@

dt[28, 1] <- c("Hypertension (%) [note]")
dt[32, 1] <- c("Carbohydrate\npercent (%) [note]")
dt[35, 1] <- c("DM [note]")
dt[36, 1] <- c("Physical\nactivity (hours/day) [note]")

kable(dt,  align = "l", escape = F, row.names = FALSE,
              format = "html", caption = "Means, percentages, and 95% CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  add_indent(c(3:6, 9, 10, 12:19, 23:25, 27, 29)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.", 
                       "Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.", 
                       "Glucose and A1C levels are estimated in subgroups of people without diabetes.")) %>% 
  add_footnote(c("For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted Pearson Chi-2 test for survey data.",
                 "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.", 
                 "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 "DM was defined by A1C > 6.5%.", 
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity during the survey."), 
               notation = "symbol")
```

### 2018-07-28 results/posterior analysis.Rmd
tables 1 added

blood78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")
blood56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_indiv.dta")
blood14 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_indiv_uk.dta")

@@

BMI78 <- blood78 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime, 
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, cluster1, cluster2, cluster3, 
         cluster4, cluster5, area, gor) %>% 
  rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
  mutate(Years = "7-8") %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1, 
                                 MVPAtime = -4)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1,
                                 drink = -8)) %>% 
    replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))

>>>>

blood78 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")
# blood78 <- read_dta("~/Documents/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr7-8a_indiv.dta")

blood56 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr5-6a_indiv.dta")
blood14 <- read_dta("~/Downloads/UKDA-6533-stata11_se/stata11_se/ndns_rp_yr1-4a_indiv_uk.dta")

@@

BMI78 <- blood78 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2,  
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, cluster1, cluster2, cluster3, 
         cluster4, cluster5, area, gor) %>% 
  rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
  mutate(Years = "7-8", MVPAtime = NA) %>% 
  replace_with_na(replace = list(bmival = -1, 
                                 wstval = -1, 
                                 bpmedd2 = -1, 
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 cigsta3 = -1)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1,
                                 drink = -8)) %>% 
    replace_with_na(replace = list(drink = -9,
                                 cigsta3 = -8))
